Addressing climate change and development pressures in an urban estuary through habitat restoration planning

### 2022-08-22 manu-draft.qmd
inter and supratidal habitat change analysis table done

load(file = here('tabs/subttab.RData'))
```

@@

@@

Table 2: Land use change table

>>>>

load(file = here('tabs/subttab.RData'))
load(file = here('tabs/acretab.RData'))
```

@@

Table 2

@@

```{r}
#| tbl-cap: Change over time in hectares for intertidal and supratidal habitats in Tampa Bay.  Columns show years with available data and the final two columns show the change and percent change from 1990 to 2017.
acretab
```
